Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-12 paper-v1.tex
new changes in Design

A thorny issue in the academic system that can and should be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}. 

@@

Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials. It's worth mentioning: Publons\cite{Publons}a service integrated with ORCID (researcher identifier) that provides peer-review metric; Peerage of Science\cite{Peerage}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.

\section{System concept}
In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors. We imagine a final paper originating from the peer-review process as a complex system that emerges from the interactions between the authors and the reviewers, a whole that is more than the sum of its parts. Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
\newline A previous version of this paper can be found here \cite{AntsReview}. 
\newline Its design and implementation are exposed in the following section.
\subsection{Design}
Here we describe the main features of AntsReview:
\begin{itemize}
\item \emph{accountability}: both for recognition and for security against fraud and abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest. This means the platform acts like a version control system where commits are permanent and their hashes timestamped; 
\item \emph{transparency of the records}: all reviews should be open access to the community ('open report') to prevent waste of knowledge and disrupt the obscure system of black boxes of peer reviews in journals that centralize all the reports;
\item \emph{incentivisation}: via symbolic and material recognition of the performed work. reputation and bounties;
\item \emph{inclusiveness via gamification}: all the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
\end{itemize}

>>>>

\newline A thorny issue in the academic system that can and should be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}. 

@@

\newline Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials. It's worth mentioning: Publons\cite{Publons}a service integrated with ORCID (researcher identifier) that provides peer-review metric; Peerage of Science\cite{Peerage}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.

\section{System concept}
In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors. We imagine a final paper originating from the peer-review process as a complex system that emerges from the interactions between the authors and the reviewers, a whole that is more than the sum of its parts. Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
\newline A previous version of this paper can be found here \cite{AntsReview}. 
\newline Its design and implementation are exposed in the following section.

\subsection{Design}

\emph{Incentivisation.} A typical business model for open source software (OSS) movement is open-source bounty. Bounties are a prize or monetary reward given for completing a task before a deadline. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are Gitcoin \cite{Gitcoin} and The Bounties Network \cite{Bounty}. Incentives can be cryptographic tokens, unit of values registered on a blockchain network and that represent the quantity and quality of a service within a network. 
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals)  should be able to retribute with tokens, an internal cryptocurrency that can be spent externally. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher. 
Thus, the system acts also as a reputation builder.
\newline \emph{Transparency of the records} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community ('open report') even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge. following the example of models of 'cascading' or 'portable peer-reviews' offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium and independent companies like ResearchSquare and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable

Here we describe the main features of AntsReview:
\begin{itemize}
\item \emph{accountability}: both for recognition and for security against fraud and abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest. This means the platform acts like a version control system where commits are permanent and their hashes timestamped; 
\item \emph{transparency of the records}: all reviews should be open access to the community ('open report') to prevent waste of knowledge and disrupt the obscure system of black boxes of peer reviews in journals that centralize all the reports;
\item \emph{incentivisation}: 
\item \emph{inclusiveness via gamification}: all the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
\end{itemize}
